Modular Synthesis of Verified Verifiers of Computation with STV Algorithms

### 2019-03-14 paper/paper.tex
repetition of "vary widely"

This informal description is necessarily imprecise, with details differing widely between jurisdictions. For example,
the details of precisely which excess ballots are being transferred after candidates have been elected, the order in which surplus ballots are being transferred vary widely between different jurisdictions.

>>>>

This informal description is necessarily imprecise, with details
differing widely between jurisdictions. For example, there are
substantial differences in the details of
precisely which excess ballots are being transferred after
candidates have been elected, or  the order in which surplus ballots are
being transferred.
